New Evidence on the Soft Budget Constraint: Chinese Environmental Policy Effectiveness in Private versus SOEs

### 2020-02-23 Paper/No_author.tex
updates before submitting to Public Choices

\title{New Evidence on the Soft Budget Constraint: Chinese Environmental Policy Effectiveness in Private versus SOEs\thanks{We would like to thank Zhao Ruili and Zhou Ling for their precious help in collecting the data from the China Environment Statistics Yearbook.}}
\author{
Mathilde Maurel\thanks{CNRS, France and Centre d'Economie de la Sorbonne, Université Paris 1 Panthéon-Sorbonne, France} 
\and Thomas Pernet\thanks{Centre d'Economie de la Sorbonne, Université Paris 1 Panthéon-Sorbonne, France,
\href{mailto:t.pernetcoudrier@gmail.com}{email: t.pernetcoudrier@gmail.com} 
%email: \href{t.pernetcoudrier@gmail.com}
}
}

>>>>

\title{New Evidence on the Soft Budget Constraint: Chinese Environmental Policy Effectiveness in Private versus SOEs}
\author{}
